---
title: "let's apply immunarch"
author: "Tess Attenborough"
date: "22/06/2020"
output: html_document
---

```{r}
library(dplyr)
library(immunarch)
library("devtools")
library("ggplot2")
library("vegan")
library("ineq")
library("tidyverse")
library("praise")
library("scales")
library("patchwork")
library("ghibli")

```


clonality by on of off treatment in PTI group:aall
```{r}

cd4Palette <- c("#E69F00", "#56B4E9")
cd8Palette <- c("#D55E00","#0072B2")

p1 = vis(.data = immalpha, .by = c("Status", "Week"), .meta = alphaCDR3CD4dataBeginningAndEnd$meta, .test = TRUE, .plot = "box")+   # ghibli stuff
  scale_fill_ghibli_d("YesterdayMedium", direction = -1)
p1
fixVis(p1)

immalpha= repClonality(alphaCDR3CD4dataPTI$data, "homeo")
immalpha
p1 = vis(.data = immalpha, .by = "ART", .meta = alphaCDR3CD4dataPTI$meta,  .plot = "box")+scale_fill_manual(values=cd4Palette)
p1
fixVis(p1)
ggsave("alphaCD4byPTIImmune.pdf", width = 35, height = 25, units = c('cm')) #clonality by pti patients on and off treatment

immalpha= repClonality(betaCDR3CD4dataPTI$data, "homeo")
immalpha
p2 = vis(.data = immalpha, .by = "ART", .meta = betaCDR3CD4dataPTI$meta)+scale_fill_manual(values=cd4Palette)
p2
fixVis(p2)
ggsave("betaCD4byPTIImmune.pdf", width = 35, height = 25, units = c('cm')) #clonality by pti patients on and off treatment

immalpha= repClonality(alphaCDR3CD8dataPTI$data, "homeo")
immalpha
p3 = vis(.data = immalpha, .by = "ART", .meta = alphaCDR3CD8dataPTI$meta)+scale_fill_manual(values=cd8Palette)
p3
fixVis(p3)
ggsave("alphaCD8byPTIImmune.pdf", width = 35, height = 25, units = c('cm')) #clonality by pti patients on and off treatment

immalpha= repClonality(betaCDR3CD8dataPTI$data, "homeo")
immalpha
p4 = vis(.data = immalpha, .by = "ART", .meta = betaCDR3CD8dataPTI$meta)+scale_fill_manual(values=cd8Palette)
p4
fixVis(p4)
ggsave("betaCD8byPTIImmune.pdf", width = 35, height = 25, units = c('cm')) #clonality by pti patients on and off treatment

p1 + p2+ p3 + p4 +
  plot_layout(guides = 'collect')
vis

ggsave("on_or_off_ART_clonality.pdf", width = 35, height = 45, units = c('cm'))
```

v and j gene usage in cd4
```{r}
##alpha ve gene in CD4
imm_gu <- geneUsage(alphaVDJCD4data$data, "hs.trav", .norm = T, .quant = "count")
imm_gu
vis(imm_gu, .by = "ART", .meta = alphaVDJCD4data$meta)
ggsave("test1.pdf", width = 55, height = 45, units = c('cm'))
vis(imm_gu, .by = "ART", .meta = alphaVDJCD4data$meta, .plot = "box")
ggsave("test2.pdf", width = 55, height = 45, units = c('cm'))
vis(imm_gu, .by = "ART", .meta = alphaVDJCD4data$meta, .plot = "box")
ggsave("alphaCD4VbyImmune.pdf", width = 55, height = 45, units = c('cm'))

##beta ve gene in CD4
imm_gu <- geneUsage(betaVDJCD4data$data, "hs.trbv", .norm = T, .quant = "count")
imm_gu
vis(imm_gu, .by = "ART", .meta = betaVDJCD4data$meta, .plot = "box")
ggsave("betaCD4VbyImmune.pdf", width = 55, height = 45, units = c('cm'))

##alpha j gene in CD4
imm_gu <- geneUsage(alphaVDJCD4data$data, "hs.traj", .norm = T, .quant = "count")
imm_gu
vis(imm_gu, .by = "ART", .meta = alphaVDJCD4data$meta, .plot = "box")
ggsave("alphaCD4JbyImmune.pdf", width = 55, height = 45, units = c('cm'))

##beta j gene in CD4
imm_gu <- geneUsage(betaVDJCD4data$data, "hs.trbj", .norm = T, .quant = "count")
imm_gu
vis(imm_gu, .by = "ART", .meta = betaVDJCD4data$meta, .plot = "box")
ggsave("betaCD4JbyImmune.pdf", width = 55, height = 45, units = c('cm'))
```

v and j gene usage in CD8
```{r}
##alpha ve gene in CD8
imm_gu <- geneUsage(alphaVDJCD8data$data, "hs.trav", .norm = T, .quant = "count")
imm_gu
vis(imm_gu, .by = "ART", .meta = alphaVDJCD8data$meta, .plot = "box")
ggsave("alphaCD8VbyImmune.pdf", width = 55, height = 45, units = c('cm'))

##beta ve gene in CD8
imm_gu <- geneUsage(betaVDJCD8data$data, "hs.trbv", .norm = T, .quant = "count")
imm_gu
vis(imm_gu, .by = "ART", .meta = betaVDJCD8data$meta, .plot = "box")
ggsave("betaCD8VbyImmune.pdf", width = 55, height = 45, units = c('cm'))

##alpha j gene in CD8
imm_gu <- geneUsage(alphaVDJCD8data$data, "hs.traj", .norm = T, .quant = "count")
imm_gu
vis(imm_gu, .by = "ART", .meta = alphaVDJCD8data$meta, .plot = "box")
ggsave("alphaCD8JbyImmune.pdf", width = 55, height = 45, units = c('cm'))

##beta j gene in CD8
imm_gu <- geneUsage(betaVDJCD8data$data, "hs.trbj", .norm = T, .quant = "count")
imm_gu
vis(imm_gu, .by = "ART", .meta = betaVDJCD8data$meta, .plot = "box")
ggsave("betaCD8JbyImmune.pdf", width = 55, height = 45, units = c('cm'))
```

v and j gene usage in cd4 NOT INCLUDING ABUNDANCE COUNT
```{r}
##alpha ve gene in CD4
imm_gu <- geneUsage(alphaVDJCD4data$data, "hs.trav", .norm = T, .quant = "NA")
imm_gu
p1 = vis(imm_gu, .by = "ART", .meta = alphaVDJCD4data$meta, .plot = "box", .test = FALSE)+scale_fill_manual(values=cd4Palette)
fixVis(p1)
ggsave("alphaCD4VbyImmuneNoCount.pdf", width = 40, height = 25, units = c('cm'))

##beta ve gene in CD4
imm_gu <- geneUsage(betaVDJCD4data$data, "hs.trbv", .norm = T, .quant = "NA")
imm_gu
p1 = vis(imm_gu, .by = "ART", .meta = betaVDJCD4data$meta, .plot = "box", .test = FALSE)+scale_fill_manual(values=cd4Palette)
fixVis(p1)
ggsave("betaCD4VbyImmuneNoCount.pdf", width = 40, height = 25, units = c('cm'))

##alpha j gene in CD4
imm_gu <- geneUsage(alphaVDJCD4data$data, "hs.traj", .norm = T, .quant = "NA")
imm_gu
p1 = vis(imm_gu, .by = "ART", .meta = alphaVDJCD4data$meta, .plot = "box", .test = FALSE)+scale_fill_manual(values=cd4Palette)
fixVis(p1)
ggsave("alphaCD4JbyImmuneNoCount.pdf", width = 40, height = 25, units = c('cm'))

##beta j gene in CD4
imm_gu <- geneUsage(betaVDJCD4data$data, "hs.trbj", .norm = T, .quant = "NA")
imm_gu
p1 = vis(imm_gu, .by = "ART", .meta = betaVDJCD4data$meta, .plot = "box", .test = FALSE)+scale_fill_manual(values=cd4Palette)
fixVis(p1)
ggsave("betaCD4JbyImmuneNoCount.pdf", width = 40, height = 25, units = c('cm'))
```

v and j gene usage in CD8 NOT INCLUDING ABUNDANCE COUNT
```{r}
##alpha ve gene in CD8
imm_gu <- geneUsage(alphaVDJCD8data$data, "hs.trav", .norm = T, .quant = "NA")
imm_gu
p1 = vis(imm_gu, .by = "ART", .meta = alphaVDJCD8data$meta, .plot = "box", .test = FALSE)+scale_fill_manual(values=cd8Palette)
fixVis(p1)
ggsave("alphaCD8VbyImmuneNoCount.pdf", width = 40, height = 25, units = c('cm'))

##beta ve gene in CD8
imm_gu <- geneUsage(betaVDJCD8data$data, "hs.trbv", .norm = T, .quant = "NA")
imm_gu
p1 = vis(imm_gu, .by = "ART", .meta = betaVDJCD8data$meta, .plot = "box", .test = FALSE)+scale_fill_manual(values=cd8Palette)
fixVis(p1)
ggsave("betaCD8VbyImmuneNoCount.pdf", width = 40, height = 25, units = c('cm'))

##alpha j gene in CD8
imm_gu <- geneUsage(alphaVDJCD8data$data, "hs.traj", .norm = T, .quant = "NA")
imm_gu
p1 = vis(imm_gu, .by = "ART", .meta = alphaVDJCD8data$meta, .plot = "box", .test = FALSE)+scale_fill_manual(values=cd8Palette)
fixVis(p1)
ggsave("alphaCD8JbyImmuneNoCount.pdf", width = 40, height = 25, units = c('cm'))

##beta j gene in CD8
imm_gu <- geneUsage(betaVDJCD8data$data, "hs.trbj", .norm = T, .quant = "NA")
imm_gu
p1 = vis(imm_gu, .by = "ART", .meta = betaVDJCD8data$meta, .plot = "box", .test = FALSE)+scale_fill_manual(values=cd8Palette)
fixVis(p1)
ggsave("betaCD8JbyImmuneNoCount.pdf", width = 40, height = 25, units = c('cm'))
```

jensen shannon divergense in gene usage - no count included
```{r}
#cd4
imm_gu <- geneUsage(alphaVDJCD4data$data, "hs.trav", .norm = T, .quant = "NA") # alpha CD4 V gene
imm_gu_js <- geneUsageAnalysis(imm_gu, .method = "js", .verbose = F)
p1 <- vis(imm_gu_js, .title = "Gene usage JS-divergence: CD4 alpha V gene", .leg.title = "JS", .text.size = 1.5)
p1
ggsave("alphaCD4VJensenShannonNoCount.pdf", width = 25, height = 15, units = c('cm'))

imm_gu <- geneUsage(betaVDJCD4data$data, "hs.trbv", .norm = T, .quant = "NA") # beta CD4 V gene
imm_gu_js <- geneUsageAnalysis(imm_gu, .method = "js", .verbose = F)
p2 <- vis(imm_gu_js, .title = "Gene usage JS-divergence: CD4 beta V gene", .leg.title = "JS", .text.size = 1.5)
p2
ggsave("betaCD4VJensenShannonNoCount.pdf", width = 25, height = 15, units = c('cm'))

imm_gu <- geneUsage(alphaVDJCD4data$data, "hs.traj", .norm = T, .quant = "NA") # alpha CD4 J gene
imm_gu_js <- geneUsageAnalysis(imm_gu, .method = "js", .verbose = F)
p3 <- vis(imm_gu_js, .title = "Gene usage JS-divergence: CD4 alpha J gene", .leg.title = "JS", .text.size = 1.5)
p3
ggsave("alphaCD4JJensenShannonNoCount.pdf", width = 25, height = 15, units = c('cm'))

imm_gu <- geneUsage(betaVDJCD4data$data, "hs.trbj", .norm = T, .quant = "NA") # beta CD4 J gene
imm_gu_js <- geneUsageAnalysis(imm_gu, .method = "js", .verbose = F)
p4 <- vis(imm_gu_js, .title = "Gene usage JS-divergence: CD4 beta J gene", .leg.title = "JS", .text.size = 1.5)
p4
ggsave("betaCD4JJensenShannonNoCount.pdf", width = 25, height = 15, units = c('cm'))

p1 + p3+ p2 + p4 +
  plot_layout(guides = 'collect')


ggsave("CD4JensenShannonNoCount.pdf", width = 38, height = 30, units = c('cm'))

#########################################
#CD8
imm_gu <- geneUsage(alphaVDJCD8data$data, "hs.trav", .norm = T, .quant = "NA") # alpha CD8 V gene
imm_gu_js <- geneUsageAnalysis(imm_gu, .method = "js", .verbose = F)
p1 <- vis(imm_gu_js, .title = "Gene usage JS-divergence: CD8 alpha V gene", .leg.title = "JS", .text.size = 1.5)
p1
ggsave("alphaCD8VJensenShannonNoCount.pdf", width = 25, height = 15, units = c('cm'))

imm_gu <- geneUsage(betaVDJCD8data$data, "hs.trbv", .norm = T, .quant = "NA") # beta CD8 V gene
imm_gu_js <- geneUsageAnalysis(imm_gu, .method = "js", .verbose = F)
p1 <- vis(imm_gu_js, .title = "Gene usage JS-divergence: CD8 beta V gene", .leg.title = "JS", .text.size = 1.5)
p1
ggsave("betaCD8VJensenShannonNoCount.pdf", width = 25, height = 15, units = c('cm'))

imm_gu <- geneUsage(alphaVDJCD8data$data, "hs.traj", .norm = T, .quant = "NA") # alpha CD8 J gene
imm_gu_js <- geneUsageAnalysis(imm_gu, .method = "js", .verbose = F)
p1 <- vis(imm_gu_js, .title = "Gene usage JS-divergence: CD8 alpha J gene", .leg.title = "JS", .text.size = 1.5)
p1
ggsave("alphaCD8JJensenShannonNoCount.pdf", width = 25, height = 15, units = c('cm'))

imm_gu <- geneUsage(betaVDJCD8data$data, "hs.trbj", .norm = T, .quant = "NA") # beta CD8 J gene
imm_gu_js <- geneUsageAnalysis(imm_gu, .method = "js", .verbose = F)
p1 <- vis(imm_gu_js, .title = "Gene usage JS-divergence: CD8 beta J gene", .leg.title = "JS", .text.size = 1.5)
p1
ggsave("betaCD8JJensenShannonNoCount.pdf", width = 25, height = 15, units = c('cm'))

```


beginning and end time points
```{r}
immalpha= repClonality(alphaCDR3CD4dataBeginningAndEnd$data, "homeo")
immalpha
p1 = vis(.data = immalpha, .by = c("Status", "Week"), .meta = alphaCDR3CD4dataBeginningAndEnd$meta, .test = TRUE, .plot = "box")+   # ghibli stuff
  scale_fill_ghibli_d("YesterdayMedium", direction = -1)
p1
fixVis(p1)
ggsave("alphaCD4byBeginningAndEnd.pdf", width = 35, height = 25, units = c('cm')) #clonality start and end alpha cd4

immalpha= repClonality(betaCDR3CD4dataBeginningAndEnd$data, "homeo")
immalpha
p2 = vis(.data = immalpha, .by = c("Status", "Week"), .meta = betaCDR3CD4dataBeginningAndEnd$meta, .test = TRUE)+
  # ghibli stuff
  scale_fill_ghibli_d("YesterdayMedium", direction = -1)
p2
fixVis(p2)
ggsave("betaCD4byBeginningAndEnd.pdf", width = 35, height = 25, units = c('cm')) #clonality start and end beta cd4

immalpha= repClonality(alphaCDR3CD8dataBeginningAndEnd$data, "homeo")
immalpha
p3 = vis(.data = immalpha, .by = c("Status", "Week"), .meta = alphaCDR3CD8dataBeginningAndEnd$meta, .test = TRUE)+
  # ghibli stuff
  scale_fill_ghibli_d("LaputaMedium", direction = -1)
p3
fixVis(p3)
ggsave("alphaCD8byBeginningAndEnd.pdf", width = 35, height = 25, units = c('cm')) #clonality start and end alpha cd8

immalpha= repClonality(betaCDR3CD8dataBeginningAndEnd$data, "homeo")
immalpha
p4 = vis(.data = immalpha, .by = c("Status", "Week"), .meta = betaCDR3CD8dataBeginningAndEnd$meta, .test = TRUE)+
  # ghibli stuff
  scale_fill_ghibli_d("LaputaMedium", direction = -1)
ggsave("betaCD8byBeginningAndEnd.pdf", width = 35, height = 25, units = c('cm')) #clonality start and end beta cd8
p4

fixVis(p4)
p1 + p2+ p3 + p4 +
  plot_layout(guides = 'collect')
vis

ggsave("start_and_end_clonality.pdf", width = 35, height = 45, units = c('cm'))
```

here i'm going to do spectratypes of patient K's CD4 and CD8 beta chain samples
```{r}

Spectratyping (Patient K CD4+ Week 0)
CDR3 length (aa)
Sequence count
p1 <- vis(spectratype(betaCDR3CD4dataPTI$data[[1]], .quant = "id", .col = "aa")) #this does not include abundance, like heather 2018
p1
fixVis(p1)
p2 <- vis(spectratype(betaCDR3CD4dataPTI$data[[2]], .quant = "id", .col = "aa")) #this does not include abundance, like heather 2018
p2

fixVis(p2)
p3 <- vis(spectratype(betaCDR3CD4dataPTI$data[[3]], .quant = "id", .col = "aa")) #this does not include abundance, like heather 2018
p3
fixVis(p3)
p4 <- vis(spectratype(betaCDR3CD4dataPTI$data[[4]], .quant = "id", .col = "aa")) #this does not include abundance, like heather 2018
p4
fixVis(p4)
p1 + p3+ p2 + p4 +
  plot_layout(guides = 'collect')


ggsave("spectra_K_cd4_beta.pdf", width = 38, height = 30, units = c('cm'))

p1 <- vis(spectratype(betaCDR3CD8dataPTI$data[[1]], .quant = "id", .col = "aa")) #this does not include abundance, like heather 2018
p1
fixVis(p1)

p2 <- vis(spectratype(betaCDR3CD8dataPTI$data[[2]], .quant = "id", .col = "aa")) #this does not include abundance, like heather 2018
p2
fixVis(p2)
p3 <- vis(spectratype(betaCDR3CD8dataPTI$data[[3]], .quant = "id", .col = "aa")) #this does not include abundance, like heather 2018
p3
fixVis(p3)
p4 <- vis(spectratype(betaCDR3CD8dataPTI$data[[4]], .quant = "id", .col = "aa")) #this does not include abundance, like heather 2018
p4
fixVis(p4)

p1 + p3+ p2 + p4 +
  plot_layout(guides = 'collect')

Spectratyping (Patient K CD8+ Week 0)
CDR3 length (aa)
Sequence count

ggsave("spectra_K_cd8_beta.pdf", width = 38, height = 30, units = c('cm'))

#experiment - spectrac by week?? doesn't work as it uses raw numbers
exp_len <- repExplore(betaCDR3CD4data$data, .method = "len", .col = "aa")
p1 <- vis(exp_len, .by = "Week", .meta = betaCDR3CD4data$meta)
p1

```

clonotype tracking
```{r}
tc1 <- trackClonotypes(betaCDR3CD8data$data, list(1, 10), .col = "aa")
tc1
p1 <- vis(tc1)
p1

tc1 <- trackClonotypes(betaCDR3CD8dataPTI$data, list(1, 10), .col = "aa")
tc1
p1 <- vis(tc1)
p1

tc1 <- trackClonotypes(betaCDR3CD8dataPTI$data, list(5, 10), .col = "aa")
tc1
p2 <- vis(tc1)
p2

tc1 <- trackClonotypes(betaCDR3CD8dataPTI$data, list(9, 10), .col = "aa")
tc1
p3 <- vis(tc1)
p3

tc1 <- trackClonotypes(betaCDR3CD8dataPTI$data, list(13, 10), .col = "aa")
tc1
p4 <- vis(tc1)
p4
```

tracking the top 10 cdr3 seqs in cd4 alpha

```{r}


tc1 <- trackClonotypes(alphaCDR3CD4data$data, list(3, 10), .col = "aa") #F
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD4top10from0F.pdf", width = 35, height = 25, units = c('cm'))


tc1 <- trackClonotypes(alphaCDR3CD4data$data, list(5, 10), .col = "aa") #K
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD4top10from0K.pdf", width = 35, height = 25, units = c('cm')) 


tc1 <- trackClonotypes(alphaCDR3CD4data$data, list(9, 10), .col = "aa") #L
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD4top10from0L.pdf", width = 35, height = 25, units = c('cm')) #clonality start and end alpha cd4

tc1 <- trackClonotypes(alphaCDR3CD4data$data, list(12, 10), .col = "aa") #P
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD4top10from0P.pdf", width = 35, height = 25, units = c('cm')) #clonality start and end alpha cd4

tc1 <- trackClonotypes(alphaCDR3CD4data$data, list(14, 10), .col = "aa") #Q
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD4top10from0Q.pdf", width = 35, height = 25, units = c('cm')) #clonality start and end alpha cd4

tc1 <- trackClonotypes(alphaCDR3CD4data$data, list(18, 10), .col = "aa") #T
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD4top10from0T.pdf", width = 35, height = 25, units = c('cm')) #clonality start and end alpha cd4

```
tracking the top 10 cdr3 seqs in cd4 beta
```{r}
tc1 <- trackClonotypes(betaCDR3CD4data$data, list(1, 10), .col = "aa") #D
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD4top10from0D.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD4data$data, list(3, 10), .col = "aa") #E
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD4top10from0E.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD4data$data, list(5, 10), .col = "aa") #F
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD4top10from0F.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD4data$data, list(7, 10), .col = "aa") #K
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD4top10from0K.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD4data$data, list(11, 10), .col = "aa") #L
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD4top10from0L.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD4data$data, list(15, 10), .col = "aa") #P
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD4top10from0P.pdf", width = 35, height = 25, units = c('cm'))


tc1 <- trackClonotypes(betaCDR3CD4data$data, list(17, 10), .col = "aa") #Q
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD4top10from0Q.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD4data$data, list(19, 10), .col = "aa") #T
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD4top10from0T.pdf", width = 35, height = 25, units = c('cm'))

```
tracking the top 10 cdr3 seqs in cd8 alpha
```{r}
tc1 <- trackClonotypes(alphaCDR3CD8data$data, list(1, 10), .col = "aa") #E
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD8top10from0E.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(alphaCDR3CD8data$data, list(3, 10), .col = "aa") #F
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD8top10from0F.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(alphaCDR3CD8data$data, list(5, 10), .col = "aa") #K
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD8top10from0K.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(alphaCDR3CD8data$data, list(9, 10), .col = "aa") #L
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD8top10from0L.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(alphaCDR3CD8data$data, list(14, 10), .col = "aa") #Q
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD8top10from0Q.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(alphaCDR3CD8data$data, list(18, 10), .col = "aa") #T
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD8top10from0T.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(alphaCDR3CD8data$data, list(21, 10), .col = "aa") #V
tc1
p1 <- vis(tc1)
p1
ggsave("alphaCD8top10from0V.pdf", width = 35, height = 25, units = c('cm'))

```

tracking the top 10 cdr3 seqs in cd8 beta
```{r}
tc1 <- trackClonotypes(betaCDR3CD8data$data, list(1, 10), .col = "aa") #E
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD8top10from0E.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD8data$data, list(3, 10), .col = "aa") #F
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD8top10from0F.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD8data$data, list(5, 10), .col = "aa") #K
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD8top10from0K.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD8data$data, list(9, 10), .col = "aa") #L
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD8top10from0L.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD8data$data, list(14, 10), .col = "aa") #Q
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD8top10from0Q.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD8data$data, list(18, 10), .col = "aa") #T
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD8top10from0T.pdf", width = 35, height = 25, units = c('cm'))

tc1 <- trackClonotypes(betaCDR3CD8data$data, list(22, 10), .col = "aa") #V
tc1
p1 <- vis(tc1)
p1
ggsave("betaCD8top10from0V.pdf", width = 35, height = 25, units = c('cm'))

```
going to look at k-mers
```{r}
kmers <- getKmers(alphaCDR3CD4data$data, 5)
vis(kmers, .by = "Week", .meta = alphaCDR3CD4data$meta)

p2 <- vis(kmers, .position = "fill", .by = "Week", .meta = alphaCDR3CD4data$meta)
p2
ggsave("kmersCD4alpha.pdf", width = 35, height = 25, units = c('cm'))


imm.km <- getKmers(alphaCDR3CD4dataPTI$data, 5)
p2 <- vis(imm.km, .by = "ART", .meta = alphaCDR3CD4dataPTI$meta)
p2

#not enormously helpful as I can't separate by treatment

```


now for some ordination
```{r}
imm_ov1 <- repOverlap(betaCDR3CD8data$data, .method = "jaccard", .verbose = F)
p1 <- vis(imm_ov1)
imm_ov1
p1
repOverlapAnalysis(imm_ov1, "tsne") %>% vis()

#not sure if useful/intertewsting
```

public clonotypes
```{r}
pr.aa <- pubRep(betaCDR3CD8data$data, "aa", .verbose = F) #show abundance/appearance in all samples
pr.aa

pr1 <- pubRepFilter(pr.aa, betaCDR3CD8data$meta, c(Week = 12), .min.samples = 2) #selects sequences which appear in at least two off-treatemtn samples
pr1

pr1 <- pubRepFilter(pr.aa, betaCDR3CD8data$meta, c(ART = "Off"), .min.samples = 2) #selects sequences which appear in at least two off-treatemtn samples
pr1
write.csv(pr1, "cd8betaPublicOffART.csv")

pr2 <- pubRepFilter(pr.aa, betaCDR3CD8data$meta, c(ART = "On")) #all on treatment samples
pr2

pr3 <- pubRepFilter(pr.aa, betaCDR3CD8data$meta, c(Status = "CT")) #all on treatment samples
pr3 #CT only

testio = anti_join(pr1, pr2, by = "CDR3.aa") #only the elements of pr1 that aren't also in pr2
write.csv(testio, "cd8betaPublicOffARTNotInOff.csv")
testio

testio2 = anti_join(testio, pr3, by = "CDR3.aa") #only the elements of testio that aren't also in pr3
write.csv(testio2, "cd8betaPublicOffARTNotInOfforNA.csv")
testio2

# take out known samples
testio2_3s <- testio2[testio2$Samples >2,]

testio2 <- testio2[!testio2$Samples >2,]

# take out rest
comTab <- complete.cases(testio2[,3:4]) | complete.cases(testio2[,5:6]) | complete.cases(testio2[,7:8]) | complete.cases(testio2[,9:10])




target <- c("CASSLAGNTIYF", "CASSLGVGAAYEQYF", "CASSLQGRDEQFF", "CSALGRDYTF", "CASSDETGASYEQYF")
tc <- trackClonotypes(betaCDR3CD8data$data, target, .col = "aa")
vis(tc)
```


